---
title: "gss marriage politics analysis"
subtitle: "subtitle"
author: 
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/marital_status_political_affiliation_gss_analysis.git"
date: "April 20, 2023"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: TRUE
number-sections: TRUE
bibliography: references.bib
---

```{r}
#| include: false

#### Load Library ####
library(tidyverse)
library(janitor)
library(ggplot2)
library(RColorBrewer)
library(kableExtra)
library(knitr)
library(dplyr)
library(here)
library(RColorBrewer)
library(kableExtra)
library(patchwork)
library(readr)
library(here)

#### Import cleaned_gss_2021.csv ####
cleaned_gss_2021 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2021.csv"))

cleaned_gss_2018 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2018.csv"))

cleaned_gss_2016 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2016.csv"))

cleaned_gss_2014 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2014.csv"))
```

```{r}
#| include: false

#### Ordering ####

cleaned_gss_2021$partyid <- 
  factor(cleaned_gss_2021$partyid, 
         levels = c("Strong Democrat", "Not Very Strong Democrat", "Independent (Close to Democrat)", "Independent (Neither)", "Independent (Close to Republican)", "Not Very Strong Republican", "Strong Republican"))

cleaned_gss_2018$partyid <- 
  factor(cleaned_gss_2018$partyid, 
         levels = c("Strong Democrat", "Not Very Strong Democrat", "Independent (Close to Democrat)", "Independent (Neither)", "Independent (Close to Republican)", "Not Very Strong Republican", "Strong Republican"))

cleaned_gss_2016$partyid <- 
  factor(cleaned_gss_2016$partyid, 
         levels = c("Strong Democrat", "Not Very Strong Democrat", "Independent (Close to Democrat)", "Independent (Neither)", "Independent (Close to Republican)", "Not Very Strong Republican", "Strong Republican"))

cleaned_gss_2014$partyid <- 
  factor(cleaned_gss_2014$partyid, 
         levels = c("Strong Democrat", "Not Very Strong Democrat", "Independent (Close to Democrat)", "Independent (Neither)", "Independent (Close to Republican)", "Not Very Strong Republican", "Strong Republican"))
```

```{r}
#| include: false

#### Ordering ####

cleaned_gss_2021$marital <- 
  factor(cleaned_gss_2021$marital, 
         levels = c("Married", "Never Married", "Separated", "Divorced", "Widowed"))

cleaned_gss_2018$marital <- 
  factor(cleaned_gss_2018$marital, 
         levels = c("Married", "Never Married", "Separated", "Divorced", "Widowed"))

cleaned_gss_2016$marital <- 
  factor(cleaned_gss_2016$marital, 
         levels = c("Married", "Never Married", "Separated", "Divorced", "Widowed"))

cleaned_gss_2014$marital <- 
  factor(cleaned_gss_2014$marital, 
         levels = c("Married", "Never Married", "Separated", "Divorced", "Widowed"))
```

```{r}
#| include: false

#### Ordering ####

cleaned_gss_2021$cohort <- 
  factor(cleaned_gss_2021$cohort, 
         levels = c("Gen Z", "Millenial", "Gen X", "Boomer", "Post-War"))

cleaned_gss_2018$cohort <- 
  factor(cleaned_gss_2018$cohort, 
         levels = c("Gen Z", "Millenial", "Gen X", "Boomer", "Post-War"))

cleaned_gss_2016$cohort <- 
  factor(cleaned_gss_2016$cohort, 
         levels = c("Gen Z", "Millenial", "Gen X", "Boomer", "Post-War"))

cleaned_gss_2014$cohort <- 
  factor(cleaned_gss_2014$cohort, 
         levels = c("Millenial", "Gen X", "Boomer", "Post-War"))
```

```{r}
#| include: false

#### Ordering####

cleaned_gss_2021$polviews <- 
  factor(cleaned_gss_2021$polviews, 
         levels = c("Extremely Conservative", "Conservative", "Slightly Conservative", "Moderate", "Slightly Liberal", "Liberal", "Extremely Liberal"))

cleaned_gss_2018$polviews <- 
  factor(cleaned_gss_2018$polviews, 
         levels = c("Extremely Conservative", "Conservative", "Slightly Conservative", "Moderate", "Slightly Liberal", "Liberal", "Extremely Liberal"))

cleaned_gss_2016$polviews <- 
  factor(cleaned_gss_2016$polviews, 
         levels = c("Extremely Conservative", "Conservative", "Slightly Conservative", "Moderate", "Slightly Liberal", "Liberal", "Extremely Liberal"))

cleaned_gss_2014$polviews <- 
  factor(cleaned_gss_2014$polviews, 
         levels = c("Extremely Conservative", "Conservative", "Slightly Conservative", "Moderate", "Slightly Liberal", "Liberal", "Extremely Liberal"))
```

# Introduction

# Data {#sec-data}

## Data Management

This paper uses the R statistical programming language [@citeR], along with several packages, tidyverse [@citetidyverse], janitor [@citejanitor], here [@citehere], and [@citedplyr]. All figures in this paper were created using the packages ggplot2 [@citeggplot2] and the tables were created using knitr [@citeknitr] and kableExtra[@citekablextra]. Combinations of figures were created using [@citepatchwork] The color styling of graphs has been created using RColorBrewer [@citecolorbrewer]. The model in this paper was created using the rstanarm [@citerstanarm] package.

## Source

The data within this paper was extracted from the 2014, 2016, 2018 and 2021 United States General Social Survey (GSS). This survey is a series of nationally representative cross-sectional interviews that collects data on contemporary American society to explain and monitor trends in attitudes, opinions and behaviours [@citegsscodebook]. It began tracking these trends in 1972, and has primarily used in-person data collection as its method of data collection [@citegsscodebook]. In 2021, the survey moved to an address-based sampling method with a focus on web-based self-administered questionnaires [@citegsscodebook].

## Sampling

The United States General Social Survey (GSS) samples adults over the age of 18 in the United States who are not currently living in institutional housing [@citegsscodebook]. @tbl-1 shows the total number of responses collected by the GSS and the total number of responses used in the analysis of this paper, per year.

```{r}
#| include: false

#### Create Variable Description Tibble ####

variable_table <-
  tibble(
    "Year" = c(
      "2014",
      "2016",
      "2018",
      "2021"
    ),
    "Total # of Responses" = c(
    "2,538",
    "2,867",
    "2,348",
    "4,032"
    ),
    "Total # of Responses Used in Analysis" = c(
      "2,322",
      "2,641",
      "2,143",
      "3,529"
    )
  )
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-1
#| tbl-cap: "Number of Responses"
#### Add Variable Description Table ####
variable_table |>
  kable(booktabs = TRUE) |>
  kable_styling(font_size = 9, latex_options = "hold_position")
```

## Key Features

This paper explores the estimands, does political affiliation as measured through political views and identification impact marital status' and what influence does generational cohort and sex have. This paper explores these estimands through an analysis of the sample populations described in @tbl-1 under "Total \# of Responses Used in Analysis." Responses were removed to account for unanswered or not applicable responses. I did this to ensure the representative and completeness of all variables analyzed. The variables selected for analysis can be viewed in @tbl-2 and their measurement levels can be viewed in @tbl-3. Responses were measured using Likert scales which measure respondents' opinions to questions, and multiple choice questions.

```{r}
#| include: false

#### Create Variable Description Tibble ####

variable_table <-
  tibble(
    "Variable" = c(
      "partyid",
      "polviews",
      "marital",
      "sex",
      "cohort"
    ),
    "Variable Description" = c(
      "Self-ascribed belonging to the Republican, Democratic, or Indepedent parties",
    "Self-ascribed placement on the political spectrum from 'extremely liberal to extremely conservative'",
    "Marital status of respondent",
    "Self-ascribed sex of respondent",
    "Generational cohort that respondent belongs to "
    )
  )

```

```{r}
#| echo: false
#| warning: false
#| label: tbl-2
#| tbl-cap: "Variable Descriptions"
#### Add Variable Description Table ####
variable_table |>
  kable(booktabs = TRUE) |>
  kable_styling(font_size = 9, latex_options = "hold_position")
```

```{r}
#| include: false
#### Create Variable Measurement Tibble ####

variable_measure_table <-
  tibble(
    "Variable" = c(
      "partyid",
      "polviews",
      "marital",
      "sex",
      "cohort"
    ),
    "Variable Measurement" = c(
      "Strong Democrat, Not Very Strong Democrat, Independent (Close to Democrat), Independent (Neither), Independent (Close to Republican), Not Very Strong Republican, Strong Republican",
      "Extremely Liberal, Liberal, Slightly Liberal, Moderate, Slightly Conservative, Conservative, Extremely Conservative",
      "Married, Never Married, Separated, Divorced, Widowed",
      "Female, Male",
      "Post-War, Boomer, Gen X, Millenial, Gen Z"
    )
  )
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-3
#| tbl-cap: "Variable Measurements"
#### Add Variable Measurement Table ####
variable_measure_table |>
  kable(booktabs = TRUE) |>
  column_spec(2, width = "41em")|>
  kable_styling(font_size = 9, latex_options = "hold_position")
```

## Bias and Ethics

It is important to acknowledge that observations and data from the 2014, 2016, 2018, and 2021 US General Social Survey (GSS) may have been influenced by social trends occurring in the world around participants. These could include and are not limited to the deaths of Michael Brown and Eric Garner as a result of police brutality in 2014, the presidential election in 2016, the immigration crisis in 2018, and the continuing COVID-19 pandemic in 2021. However, this is in part, part of the importance of the GSS, to track social trends. This is why I have chosen to compare four years of survey results, to gain a better perspective of these social trends with acknowledgement of the global circumstances in which they are reported under.

One point of bias that does need to be addressed is the difference in surveying techniques. The US General Social Survey (GSS) was conducted in person in the years 2014, 2016, and 2018, however, due to the COVID-19 pandemic, it was changed to being an online survey resulting in a higher rate of non-response. The 2021 GSS controlled for this by adjusting population totals to ensure that the weighted totals closely matched the U.S. Census Bureau's estimates of sex, age, education, race, region, and ethnicity [@citegsscodebook]. Additionally, due to the survey being online, household enumeration was impossible, so households were asked to identity the adult with the most recent birthday [@citegsscodebook]. This is problematic as it may have missed some household residents who were temporarily living abroad, adult children, etc. [@citegsscodebook]. Measures were taken to control for this by conducting tests of significant to look for differences in trend estimates [@citegsscodebook]. Additionally, in the years where the survey was conducted in-person, there may have been instances of variance in how interviewers asked questions which could have led to bias in the results.

## Marital Status and Cohort

```{r}
#| include: false
#| message: false
#### Creating Graph ####
cohort_marital_2021 <- ggplot(data=cleaned_gss_2021, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Birth Cohort",
    y = "Number of Respondents",
    fill = "Marital Status",
    caption = "2021 GSS"
  ) +
  scale_fill_brewer(palette="Spectral")+
  theme(legend.position = "none") + #include legend at bottom to ensure readability when using patchwork package
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false
#### Creating Graph ####
cohort_marital_2018 <- ggplot(data=cleaned_gss_2018, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Birth Cohort",
    y = "Number of Respondents ",
    fill = "Marital Status",
    caption = "2018 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") + 
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph####
cohort_marital_2016 <- ggplot(data=cleaned_gss_2016, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Birth Cohort",
    y = "Number of Respondents",
    fill = "Marital Status",
    caption = "2016 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(legend.position = "none")+
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph ####
cohort_marital_2014 <- ggplot(data=cleaned_gss_2014, aes(x = cohort, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Birth Cohort",
    y = "Number of Respondents",
    fill = "Marital Status",
    caption = "2014 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-2
#| fig-cap: "2014-2021 Comparisons of Birth Cohort Against Respondent Marital Status"
#### Using Patchwork Package to Combine Two Graphs ####
(cohort_marital_2021) + (cohort_marital_2018) + (cohort_marital_2016) + (cohort_marital_2014) +
  plot_annotation(tag_levels = 'A') +
  plot_layout(ncol = 2)+
  plot_layout(guides = "collect")
```

## Marital Status and Self-Ascribed Belonging to Political Parties

```{r}
#| include: false
#| message: false

#### Creating Graph ####
partyid_marital_2021 <- ggplot(data=cleaned_gss_2021, aes(x = partyid, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political Identification",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2021 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph ####
partyid_marital_2018 <- ggplot(data=cleaned_gss_2018, aes(x = partyid, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political Identification",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2018 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph ####
partyid_marital_2016 <- ggplot(data=cleaned_gss_2016, aes(x = partyid, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political Identification",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2016 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph ####
partyid_marital_2014 <- ggplot(data=cleaned_gss_2014, aes(x = partyid, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political Identification",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2014 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size=6)) 
```

```{r}
#| echo: false
#| warning: false
#| label: fig-3
#| fig-cap: "2014-2021 Comparisons of Birth Cohort Against Respondent Marital Status"
#### Using Patchwork Package to Combine Two Graphs ####
(partyid_marital_2021) + (partyid_marital_2018) + (partyid_marital_2016) + (partyid_marital_2014)+ 
  plot_annotation(tag_levels = 'A') +
  plot_layout(ncol = 2)+
  plot_layout(guides = "collect")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-4
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2021 Respondents"

cleaned_gss_2021|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")

```

```{r}
#| echo: false
#| warning: false
#| label: tbl-5
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2018 Respondents"

cleaned_gss_2018|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-6
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2016 Respondents"

cleaned_gss_2016|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-7
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2014 Respondents"

cleaned_gss_2014|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

## Marital Status and Self-Ascribed Placement on Political Spectrum

```{r}
#| include: false
#| message: false

#### Creating Graph ####
polviews_marital_2021 <- ggplot(data=cleaned_gss_2021, aes(x = polviews, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political View",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2021 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph ####
polviews_marital_2018 <- ggplot(data=cleaned_gss_2018, aes(x = polviews, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political View",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2018 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph ####
polviews_marital_2016 <- ggplot(data=cleaned_gss_2016, aes(x = polviews, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political View",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2016 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  theme(text = element_text(size=6))
```

```{r}
#| include: false
#| message: false

#### Creating Graph ####
polviews_marital_2014 <- ggplot(data=cleaned_gss_2014, aes(x = polviews, fill = marital)) + #assign ggplot to new variable in order to use patchwork package later
  geom_bar(width =.8) +
  theme_classic() + 
  labs(
    x = "Political View",
    y = "# of Respondents",
    fill = "Marital Status",
    caption = "2014 GSS"
  ) +
  scale_fill_brewer(palette="Spectral") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(text = element_text(size=6))
```

```{r}
#| echo: false
#| warning: false
#| label: fig-4
#| fig-cap: "2014-2021 Comparisons of Birth Cohort Against Respondent Marital Status"
#### Using Patchwork Package to Combine Two Graphs ####
(polviews_marital_2021) + (polviews_marital_2018) + (polviews_marital_2016) + (polviews_marital_2014)+ 
  plot_annotation(tag_levels = 'A') +
  plot_layout(ncol = 2)+
  plot_layout(guides = "collect")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-8
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2014 Respondents"

cleaned_gss_2021|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-9
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2014 Respondents"

cleaned_gss_2018|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-10
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2014 Respondents"

cleaned_gss_2016|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-11
#| tbl-cap: "Marital Status vs. Self-Ascribed Belonging to Political Parties of 2014 Respondents"

cleaned_gss_2014|>
  tabyl(partyid, marital)|>
  kable(col.names = c(
    "Political Identity",
    "Married",
    "Never Married",
    "Separated",
    "Divorced",
    "Widowed"
    ),
    booktabs = TRUE,
    linesep = "")
```

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of [@citerstanarm]. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

\newpage

# References
