---
title: "gss marriage politics analysis"
subtitle: "subtitle"
author: 
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/marital_status_political_affiliation_gss_analysis.git"
date: "April 20, 2023"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: TRUE
number-sections: TRUE
bibliography: references.bib
---

```{r}
#| include: false

#### Load Library ####
library(tidyverse)
library(janitor)
library(ggplot2)
library(RColorBrewer)
library(kableExtra)
library(knitr)
library(dplyr)
library(here)
library(RColorBrewer)
library(kableExtra)
library(patchwork)
library(readr)
library(here)

#### Import cleaned_gss_2021.csv ####
cleaned_gss_2021 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2021.csv"))

cleaned_gss_2018 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2018.csv"))

cleaned_gss_2016 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2016.csv"))

cleaned_gss_2014 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2014.csv"))
```

# Introduction

# Data {#sec-data}

## Data Management

This paper uses the R statistical programming language [@citeR], along with several packages, tidyverse [@citetidy]

## Source

## Sampling

## Key Features

```{r}
#| include: false

#### Create Variable Description Tibble ####

variable_table <-
  tibble(
    "Variable" = c(
      "partyid",
      "polviews",
      "marital",
      "sex",
      "cohort"
    ),
    "Variable Description" = c(
      "Self-ascribed belonging to the Republican, Democratic, or Indepedent parties",
    "Self-ascribed placement on a Likert scale from 'extremely liberal to extremely conservative'",
    "Marital status of respondent",
    "Self-ascribed sex of respondent",
    "Generational cohort that respondent belongs to "
    )
  )

```

```{r}
#| echo: false
#| warning: false
#| label: tbl-1
#| tbl-cap: "Variable Descriptions"
#### Add Variable Table ####
variable_table |>
  kable(booktabs = TRUE) |>
  kable_styling(font_size = 9, latex_options = "hold_position")
```

```{r}
#| include: false
#### Create Variable Description Tibble ####

variable_measure_table <-
  tibble(
    "Variable" = c(
      "partyid",
      "polviews",
      "marital",
      "sex",
      "cohort"
    ),
    "Variable Measurement" = c(
      "Strong Democrat, Not Very Strong Democrat, Independent (Close to Democrat), Independent (Neither), Independent (Close to Republican), Not Very Strong Republican, Strong Republican",
      "Extremely Liberal, Liberal, Slightly Liberal, Moderate, Slightly Conservative, Conservative, Extremely Conservative",
      "Married, Never Married, Separated, Divorced, Widowed",
      "Female, Male",
      "Post-War, Boomer, Gen X, Millenial, Gen Z"
    )
  )
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-2
#| tbl-cap: "Variable Measurements"
#### Add Variable Table ####
variable_measure_table |>
  kable(booktabs = TRUE) |>
  column_spec(2, width = "41em")|>
  kable_styling(font_size = 9, latex_options = "hold_position")
```

## Bias and Ethics

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("outputs/models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

\newpage

# References
